Supplemental Information from:\\ \textit{Reconstructing the last known movements of one of Nature's giants}

### 2019-07-16 manuscript/PeerJ/blue-new-supplementary.tex
Edit figs S1 and S2

% figure s2
\begin{figure}[!htbp]
  \centering
  \includegraphics[width = \linewidth]{figures/Figure-S1-periodograms.png}
  \caption{Fourier analysis of $\delta^{15}$N values of the full (A) and behavioural phase two only (B) and behavioural phase three only (C) components of the baleen plate. Inset values are the highest frequency spectral densities (in cm). Periodic fluctuation with a distance of 13.5cm along the baleen plate is consistently recovered in behavioural phases one and two, but not in behavioural phase three.} 
  \label{figs2}
\end{figure}

>>>>

% figure s2
\begin{figure}[!htbp]
  \centering
  \includegraphics[width = \linewidth]{figures/Figure-S1-periodograms.png}
  \caption{Fourier analysis of $\delta^{15}$N values of the full (A) and behavioural phase one only (B) and behavioural phase two only (C) components of the baleen plate. Inset values are the highest frequency spectral densities (in cm). Periodic fluctuation with a distance of 13.5cm along the baleen plate is consistently recovered, but weaker in behavioural  phase one. Note that we do not separately graph behavioural phase three here because it does not show any periodicity.} 
  \label{figs2}
\end{figure}
